Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/tool.tex
Explained CC missing problem more

Our experiments used country codes returned from Team Cymru's IP to
ASN whois service \cite{cymru} to determine which ASes were registered
to which nation.  This service maintains only the most recent
registration of each AS.  To control for this possible source of
error, we retain ASes in thepath simulation, even if they were
registered more recently than the current timestamp being studied, but
we do not assign these ASes chokepoint potentials. We took this approach
because the datasets of AS registrations for the various ASN
registries tend to have more missing data at specific timestamps.
Fortunately, ASes with registration changes after each test date tend
to not be in the AS graph for that test. \Ben[inline]{Two things. 1)
  This is sort of confusing, see if you can clarify it. 2) Is this a
  big deal? How often does this happen? If it happens frequently do we
  expect it to affect our results? }

>>>>

Our experiments used country codes returned from Team Cymru's IP to
ASN whois service \cite{cymru} to determine which ASes were registered
to which nation.  This service maintains only the most recent
registration of each AS.  To control for this possible source of
error, we retain ASes in the path simulation, even if they were
registered more recently than the current timestamp being studied. This is because
the relationships of these ASes and paths through these ASes are still valid.
We do not assign these ASes chokepoint potentials, as it is not clear which nation
these ASes are registered for. We took this approach
because the datasets of AS registrations for the various ASN
registries tend to have more missing data at specific timestamps.
We do not expect this to have a considerable effect on our results
because few ASes do not have a definite nation (in the best case in the most recent
test this is less than 1\% of ASes, in the worst case in the earliest test this is around 12\% of ASes.)
Additionally, not all of the ASes that are unlinked to a nation are border ASes, and those will not
affect our results at all. Furthermore, it is unlikely that this small portion of ASes will be a majority
of border ASes for any single country, so the country level experiments are unlikely to suffer from this
hole in the data.
